surfing

### 2025-03-19 inst/surfing.Rmd
surfing citations

@farley2013 analyse surfing results using one-way ANOVA techniques and
report comparisons between the top 10 and bottom 10 surfers in the
2013 World Championship Tour and conclude that the top-ranked athletes
are more consistent than the lower-ranked group. They report that "To
date, only a limited number of research studies have reported on the
results of competitive surfing" [p44], and the analysis presented here
is hoped to change that.

>>>>

@farley2015 analyse surfing results using one-way ANOVA techniques and
report comparisons between the top 10 and bottom 10 surfers in the
2013 World Championship Tour and conclude that the top-ranked athletes
are more consistent than the lower-ranked group. They report that "To
date, only a limited number of research studies have reported on the
results of competitive surfing" [p44], and the analysis presented here
is hoped to change that.
